Developing a Visual Studio Code Language Support Extension for the Snail Programming Language

### 2023-06-06 paper.tex
feat: finish debugging history

Modern debuggers with graphical user interfaces (GUIs) include the Visual Studio Debugger, which allows a developer to track variable values, function calls, and even change pieces of code or values of expressions while debugging \cite{Microsoft_2022b}. Eclipse, a popular IDE for Java, has a similar debugger with a user friendly GUI \cite{FIXME}. Today, many developement workflows include the use of debugging tools \cite{FIXME}.

Debugging tools can be of great assistance to developers. By allowing developers to more closely and quickly inspect a program's execution, debugging tools can reduce the amount of time a developer spends debugging, and thus enhance developer productivity \cite{FIXME}.

>>>>

Modern debuggers with graphical user interfaces (GUIs) include the Visual Studio Debugger, which allows a developer to track variable values, function calls, and even change pieces of code or values of expressions while debugging \cite{Microsoft_2022b}. Eclipse, a popular IDE for Java, has a similar debugger with a user friendly GUI \cite{Sinha_2017}. Today, many developement workflows include the use of debugging tools \cite{Matloff_Salzman_2008}.

Debugging tools can be of great assistance to developers. By allowing developers to more closely and quickly inspect a program's execution, debugging tools can reduce the amount of time a developer spends debugging, and thus enhance developer productivity \cite{ZhRaAmRuWo_2008}.
